### 2023-07-04 paper/sec-dis-pseudodata.tex
Revert "Update sec-dis-pseudodata.tex"
This reverts commit cbce81e997ce92974809e520a15f7827b6f3d2bc.
sect 4

  %-----------------------------------------------------------------
\begin{table}[t]
  \centering
  \small
  \renewcommand{\arraystretch}{1.50}
\begin{tabularx}{\textwidth}{Xccccc}
\toprule
Detector &  Rapidity &  Target & Lepton sign & Acceptance  & Performance \\
\midrule
\multirow{2}{*}{FASER$\nu$}  &   &   Tungsten  & \multirow{2}{*}{muons}      &     &         \\
  &   &   (1.1 ton)  &       &     &         \\
\midrule
\multirow{2}{*}{SND@LHC}  & \multirow{2}{*}{ $7.2 \le \eta_\nu \le 8.4$}   &  Tungsten   &       &       &       \\
  &   &  (0.83 ton)   &       &       &       \\
\midrule
\midrule
\multirow{3}{*}{FASER$\nu$2}  &   & \multirow{2}{*}{Tungsten}    &   \multirow{3}{*}{only muons}     &   $E_\ell \gsim 100$ GeV  &    $\delta E_\ell \sim 30\% $     \\
  &   &  \multirow{2}{*}{(20 ton)}   &       &  $\tan \theta_\ell \lsim 0.5$   &   $\delta \theta_\ell \sim 1$ mrad      \\
  &   &     &       &  reconstructed $E_h$ \& charm ID   &  $\delta E_h \sim 30\%$        \\
\midrule
\multirow{3}{*}{AdvSND~(far)}  &   \multirow{3}{*}{ $7.2 \le \eta_\nu \le 8.4$}  &
\multirow{2}{*}{Tungsten}   &   \multirow{3}{*}{only muons}    &  $E_\mu \gsim 20 $ GeV  & \multirow{3}{*}{n/a}          \\
  &   &   \multirow{2}{*}{(5 ton)}  &        & $\theta_\mu \lsim 0.15, \theta_e \lsim 0.5$     &           \\
  &   &     &       &  reconstructed $E_h$   &           \\
\midrule
\multirow{3}{*}{FLArE}  & \multirow{3}{*}{Liquid Argon}  &  & \multirow{3}{*}{ maybe muons}  &  $E_\mu \lsim 2$ GeV, $E_e \lsim 1$ TeV    &    $\delta E_e \sim 5\% $ \\
&   &     &   & $\theta_\mu \lsim 0.4$, $\theta_e \lsim 0.5$ &    $\delta \theta_e \sim 15 $ mrad   \\
 &   &     &  & reconstructed $E_h$  &    $\delta E_h \sim 30\% $   \\
  \bottomrule
\end{tabularx}
\vspace{0.2cm}
\caption{\small For each of the far-forward LHC neutrino experiments considered
  in this work, we indicate their rapidity coverage, target material, whether
  they can identify the sign of the outgoing charged lepton,
  the detector acceptance for the charged lepton and hadronic final state,
  and the expected reconstruction performance.
  %
  We consider separately the acceptance and performance for electron and muon
  neutrinos.
  %
  Tau neutrinos have much lower production rates and are not considered in this study.
  %
  See the description of each experiment in the text for more details.
  \label{tab:FPF_experiments}
}
\end{table}
%-----------------------------------------------------------------

@@

%-----------------------------------------------------------------------
\begin{figure}[t]
    \centering
\includegraphics[width=0.9\textwidth]{plots/Nevent_FASERv2_14.pdf}
\caption{The event yields per bin $ N_{\rm ev}^{(i)}$,  Eq.~(\ref{eq:event_yields}),
  for muon neutrinos at FASER$\nu$2.
  %
  We present results binned in $x$ and $Q^2$ and integrating over the neutrino energies.
  %
  The red dot indicates the weighted center of each bin.
  %
  Adding up all bin entries results into $N_{\rm ev}(\nu_\mu)\sim 3\times 10^5 $ reconstructed muon
  neutrinos. }
    \label{fig:fasernu2_muon}
\end{figure}
%-----------------------------------------------------------------------

>>>>

  %-----------------------------------------------------------------
\begin{table}[t]
  \centering
  \small
  \renewcommand{\arraystretch}{1.50}
\begin{tabularx}{\textwidth}{Xccccc}
\toprule
Detector &  Rapidity &  Target & Lepton sign & Acceptance  & Performance \\
\midrule
\multirow{2}{*}{FASER$\nu$}  &   &   Tungsten  & \multirow{2}{*}{muons}      &     &         \\
  &   &   (1.1 ton)  &       &     &         \\
\midrule
\multirow{2}{*}{SND@LHC}  & \multirow{2}{*}{ $7.2 \le \eta_\nu \le 8.4$}   &  Tungsten   &       &       &       \\
  &   &  (0.83 ton)   &       &       &       \\
\midrule
\midrule
\multirow{3}{*}{FASER$\nu$2}  &   & \multirow{2}{*}{Tungsten}    &   \multirow{3}{*}{only muons}     &   $E_\ell \gsim 100$ GeV  &    $\delta E_\ell \sim 30\% $     \\
  &   &  \multirow{2}{*}{(20 ton)}   &       &  $\tan \theta_\ell \lsim 0.5$   &   $\delta \theta_\ell \sim 1$ mrad      \\
  &   &     &       &  reconstructed $E_h$ \& charm ID   &  $\delta E_h \sim 30\%$        \\
\midrule
\multirow{3}{*}{AdvSND~(far)}  &   \multirow{3}{*}{ $7.2 \le \eta_\nu \le 8.4$}  &
\multirow{2}{*}{Tungsten}   &   \multirow{3}{*}{only muons}    &  $E_\mu \gsim 20 $ GeV  & \multirow{3}{*}{n/a}          \\
  &   &   \multirow{2}{*}{(5 ton)}  &        & $\theta_\mu \lsim 0.15, \theta_e \lsim 0.5$     &           \\
  &   &     &       &  reconstructed $E_h$   &           \\
\midrule
\multirow{3}{*}{FLArE}  & \multirow{3}{*}{Liquid Argon}  &  & \multirow{3}{*}{ maybe muons}  &  $E_\mu \lsim 2$ GeV, $E_e \lsim 1$ TeV    &    $\delta E_e \sim 5\% $ \\
&   &     &   & $\theta_\mu \lsim 0.4$, $\theta_e \lsim 0.5$ &    $\delta \theta_e \sim 15 $ mrad   \\
 &   &     &  & reconstructed $E_h$  &    $\delta E_h \sim 30\% $   \\
  \bottomrule
\end{tabularx}
\vspace{0.2cm}
\caption{\small For each of the far-forward LHC neutrino experiments considered
  in this work, we indicate their rapidity coverage, target material, whether
  they can identify the sign of the outgoing charged lepton,
  the detector acceptance for the charged lepton and hadronic final state,
  and the expected reconstruction performance.
  %
  We consider separately the acceptance and performance for electron and muon
  neutrinos.
  %
  Tau neutrinos have much lower production rates and are not considered in this study.
  %
  See the description of each experiment in the text for more details.
  %
  For the projections in this work we assume that FASER$\nu$ and SND@LHC acquire data
  for the full Run III period, while FASER$nu$2, AdvSND, and FLArE take data
  for the complete HL-LHC period.
  \label{tab:FPF_experiments}
}
\end{table}
%-----------------------------------------------------------------

@@

%-----------------------------------------------------------------------
\begin{figure}[!ht]
    \centering
\includegraphics[width=0.9\textwidth]{plots/Nevent_FASERv2_14.pdf}
\caption{The event yields per bin $ N_{\rm ev}^{(i)}$,  Eq.~(\ref{eq:event_yields}),
  for muon neutrinos at FASER$\nu$2.
  %
  We present results binned in $x$ and $Q^2$ and integrating over the neutrino energies.
  %
  The red dot indicates the weighted center of each bin.
  %
  Adding up all bin entries results into $N_{\rm ev}(\nu_\mu)\sim 3\times 10^5 $ reconstructed muon
  neutrinos. }
    \label{fig:fasernu2_muon}
\end{figure}
%-----------------------------------------------------------------------

%-----------------------------------------------------------------------
\begin{figure}[!ht]
	\centering
	\includegraphics[width=\textwidth]{plots/percentage_errors.pdf}
	\caption{Estimate of the systematic uncertainties at FASER$\nu$2 coming from the final-state 
		lepton energy $E_\ell$ for the inclusive and charm productions. The different markers
		represent the charge of the incoming neutrino.
	}
	\label{fig:percentage_error_elepton}
\end{figure}
%-----------------------------------------------------------------------

### 2023-07-04 paper/sec-protonPDFs.tex
sect 4

\clearpage
\section{Impact on the proton PDFs}
\label{sec:protonPDFs}

Using the PDF4LHC21~\cite{PDF4LHCWorkingGroup:2022cjn} PDF set, the results are illustrated by comparing the fractional uncertainties of the original PDF set to those obtained after profiling. 
This is shown for the valence quark, gluon and the singlet distributions in Fig.~\ref{FASERv2_profiling} for FASER$\nu$2 pseudodata, while Fig.~\ref{FASERv_profiling} indicates the impact of FASER$\nu$. FASER$\nu$2 is observed to provide tighter constraints on the PDFs, with the effects being the most prominent for the valence and sea quark distributions.

\begin{figure}[H]
\centering
\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_dv_ratio.pdf}\\
\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\caption{The fractional uncertainties in the valence quark, gluon and singlet PDFs as a function of the momentum fraction $x$ at the scale $Q^2 = 10000 \, \textrm{GeV}^2$. The profiling is performed using the
PDF4LHC21 set and the pseudodata for FASER$\nu$2. The original uncertainty of PDF4LHC21 is
indicated by the red band, while the blue band demonstrates the profiled result.}
\label{FASERv2_profiling}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv_q2_10000_pdf_dv_ratio.pdf}\\
\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv_q2_10000_pdf_Sea_ratio.pdf}
\caption{The fractional uncertainties in the valence quark, gluon and singlet PDFs as a function of the momentum fraction $x$ at the scale $Q^2 = 10000 \, \textrm{GeV}^2$. The profiling is performed using the
PDF4LHC21 set and the pseudodata for FASER$\nu$. The original uncertainty of PDF4LHC21 is
indicated by the red band, while the blue band demonstrates the profiled result.}
\label{FASERv_profiling}
\end{figure}

>>>>

\clearpage
\section{Constraints on proton structure}
\label{sec:protonPDFs}

By means of the strategy outlined in Sect.~\ref{sec:settings}, here we study the constraints that differential neutrino DIS
cross-section measurements at the LHC have on the quark and gluon substructure of the proton.
%
In this section we assume an isoscalar free-nucleon target and neglect non-isoscalarity effects and nuclear modifications,
which are instead considered in Sect.~\ref{sec:nuclearPDFs}.
%
We present results first for the Hessian profiling of the PDF4LHC21 combination of global PDF sets
and second for the inclusion in the Monte Carlo fit NNPDF4.0.
%
We study the dependence on the result with respect to the choice of fitted dataset, the experiment considered,
the modelling of experimental systematic uncertainties, and the availability or not of charged lepton separation.

\subsection{Impact on PDF4LHC21}
\label{sec:pdf4lhc21}

For the Hessian profiling studies following the procedure of Sect.~\ref{sec:profiling}, the prior PDF set is taken to
be PDF4LHC21 NNLO, a Monte Carlo combination~\cite{Watt:2012tq,Carrazza:2015hva} of three global PDF sets (CT18~\cite{Hou:2019efy},
MSHT20~\cite{Bailey:2020ooq}, and NNPDF3.1~\cite{NNPDF:2017mvq}) for which Hessian
representations~\cite{Gao:2013bia,Carrazza:2015aoa} are also provided.
%
PDF4LHC21, being based on the combination of three modern global fits, provides a reasonable representation
of our current understanding of the proton PDFs.
%
We profile PDF4LHC21 with the various sets of LHC neutrino pseudo-data and assess the reduction
of PDF uncertainties in each case.
%
In this analysis, a tolerance of $T = \sqrt{\Delta \chi^2}=3$ is adopted, which is the average tolerance
used in the CT18 and MSHT20 Hessian determinations.
%
Note that we use a consistent perturbative accuracy in the prior PDF set and in the theoretical calculations.

In the following, we first compare the impact on PDF4LHC21 of a baseline LHC neutrino dataset and subsequently
we assess the stability of this result with respect to a range of variations of its input.

\paragraph{Baseline results.}
%
The baseline dataset is defined as follows.
%
We consider the FASER$\nu$2 experiment integrated over the full duration of the HL-LHC data-taking period,
we account both for inclusive and charm production structure functions, we consider the scenario
in which systematic errors can be neglected, and we allow for charge separation of the outgoing lepton.
%
This baseline result therefore represents the best-case scenario and quantifies the maximum impact that can be expected
on the PDFs: we then assess to which extent variations of these input choices degrade the reach of the pseudo-data.

Fig.~\ref{fig:profiling_baseline} displays the fractional uncertainties at the 68\% confidence level
for the up and down valence quarks, total quark singlet, strangeness, charm, and gluon PDFs
in PDF4LHC21 compared to the results of its profiling with this baseline LHC neutrino dataset, namely
FASER$\nu$2 with only statistical errors, both inclusive and charm structure functions,  and charge flavour
separation.
%
The same style of PDF comparisons will be adopted through this section.
%
Results are shown at $Q^2 = 10^4 \, \textrm{GeV}^2$ and the residual shift in central values
arising from the profiling is ignored.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\begin{figure}[t]
\centering
\includegraphics[width=0.32\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_dv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_g_ratio.pdf}\\
\includegraphics[width=0.32\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=0.32\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=0.32\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\caption{The fractional uncertainties (at the 68\% confidence level)
for the up and down valence quarks, total quark singlet, strangeness, charm, and gluon PDFs
in PDF4LHC21 compared to the results of its profiling with the baseline LHC neutrino dataset, namely
FASER$\nu$2 with only statistical errors, both inclusive and charm structure functions,  and charge flavour
separation.
%
Results are shown at the scale $Q^2 = 10^4 \, \textrm{GeV}^2$ and the shift in central values
is not considered.}
\label{fig:profiling_baseline}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In the following we consider the stability of the results in Fig.~\ref{fig:profiling_baseline}
with respect to the chosen experiment and integrated luminosity, the modelling of systematic
uncertainties, being able to identify or not charm production, and being able to tell part outgoing
charged leptons from anti-leptons.

\paragraph{Dependence with the experiments.}
%
Same as Fig.~\ref{fig:profiling_baseline} comparing FASER$\nu$2 with AdvSND and with FASER$\nu$.

\paragraph{Impact of systematic uncertainties.}
%
Same as Fig.~\ref{fig:profiling_baseline} for different scenarios concerning the experimental
systematic uncertainties.

\paragraph{Impact of charm production.}
%
Same as Fig.~\ref{fig:profiling_baseline} comparing the baseline LHC neutrino dataset with the results
of a profiling without the charm production structure functions.

\paragraph{The role of lepton charge separation.}
%
Same as Fig.~\ref{fig:profiling_baseline} comparing the baseline LHC neutrino dataset with the results
of a profiling without allowing for the possibility of outgoing lepton charge separation.

\subsection{Impact on NNPDF4.0}
\label{sec:nnpdf40}

Selection of the {\sc\small xFitter} results for the NNPDF case.
